What We Eval in the Shadows

### 2021-04-17 paper/main.tex
more

Table~\ref{tab:se-types} shows recorded effects. There are over 5M updates. In
terms of calls, we see assignments primarily and in terms of site definitions.
This is expected. A subsequent \eval call will turn a definition into an update.
The most dangerous side effect is variable removal, as it means that after a
call to \eval some binding in some environments will disappear. While rare, this
happens, but the vast majority comes from a single site called by the already
mentioned \c{withr::execute\_handlers} function. This makes sense as it is used
to defer evaluation of an expression to after the function exit and thus used
for clean up. In the corpus, it is used almost exclusively by the \c{tidyselect}
package for removing the reference to the current quosure environment while
interpreting a data frame column selectors.\footnote{\cf
\url{https://tidyselect.r-lib.org/}}

@@

\todo{Say somewhere that the R community commonly calls call/argument capturing
  (with substitute or match.call), Non-Standard Evaluation.}

>>>>

Table~\ref{tab:se-types} shows recorded effects. There are over 5M updates. In
terms of calls, we see assignments primarily and in terms of site definitions.
This is expected. A subsequent \eval call will turn a definition into an update.
The most dangerous side effect is variable removal, as it means that after a
call to \eval some binding in some environments will disappear. While rare, this
happens, but the vast majority comes from a single site
(\c{withr::execute\_handlers}). This makes sense as it is used to defer
evaluation of an expression to after the function exit and thus used for clean
up. It is used almost exclusively by the \c{tidyselect} package for removing the
reference to the current quosure environment while interpreting a data frame
column selectors.\footnote{\cf \url{https://tidyselect.r-lib.org/}}

@@

%\todo{Say somewhere that the R community commonly calls call/argument capturing
%(with substitute or match.call), Non-Standard Evaluation.}
